---
title: 'Class 03: Reading Data in R'
author: "Paige Charlton"
date: "2026-02-04"
output: html_document:
  toc: TRUE
  toc_float: TRUE
  number_sections: TRUE
  code_downlaod: TRUE 
  code_folding: SHOW
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


##Readind Data from CSVS

##Locally from my PC

In R, there are some differences from how running code and RMarkdown behave in terms of how they consider paths for files

  - **R Markdown** The relative path is based ointhe location of the rR markdown file **This is true for when you knit the file.**
  -**Run code line-by-line** The path is based on the project directory (assuming that you are working in a project).
  
  To alleviate any issues, when we are working from an RMarkdown, we will also set the working directory to the markdown file location/folder.
  
  
## JSON Data

```{r cincy_jobs}
cincy_jobs = jsonlite::fromJSON(
  txt = 'https://www.themuse.com/api/public/jobs?page=1&location=Cincinnati%2C%20OH',
  flatten = TRUE
)

names(cincy_jobs)


cincy_jobs_df = cincy_jobs[['results']]

dplyr::glimpse(cincy_jobs_df)

cincy_jobs_df2 = cincy_jobs_df |>
  tidyr::unnest(
    cols = c('locations'), names_repair = "unique"
  )

```

